High Contrast Coronagraphy

### 2024-09-17 src/tex/ms.tex
submit

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author{@mkenworthy}

% Abstract with filler text
\begin{abstract}
well here we are!
    Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
    Donec vehicula augue eu neque, morbi tristique senectus et netus et.
    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
    Phasellus eu tellus sit amet tortor gravida placerat.
    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
    Praesent eget sem vel leo ultrices bibendum.
    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
    Curabitur auctor semper nulla donec varius orci eget risus.
    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
    Duis eget orci sit amet orci dignissim rutrum.
\end{abstract}

% Main body with filler text
\section{Introduction}
\label{sec:intro}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
Donec vehicula augue eu neque, morbi tristique senectus et netus et.
Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
Phasellus eu tellus sit amet tortor gravida placerat.
Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
Praesent eget sem vel leo ultrices bibendum.
Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
Curabitur auctor semper nulla donec varius orci eget risus.
Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi.
Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae.
Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna.
Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante.
Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient.
Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis.
Pellentesque cursus luctus mauris \citep{Luger2021}.

\bibliography{bib}

>>>>

\documentclass[letterpaper]{ar-1col}
\usepackage{showyourwork}
\usepackage[letterpaper]{geometry}

\usepackage{natbib}
\usepackage{amsmath}
\usepackage{color}
\usepackage{hyperref}
\usepackage[version=4]{mhchem}
\usepackage{booktabs}% http://ctan.org/pkg/booktabs
\usepackage{amsmath}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\hypersetup{colorlinks=true,allcolors=[rgb]{0,0,0.8}}

\newcommand{\kms}{km~s$^{-1}$}
\newcommand{\mum}{$\mu$m}
\newcommand{\ld}{$\lambda/D$}
\newcommand{\fourier}[1]{\mathcal{F}\{#1\}}
\newcommand{\invfourier}[1]{\mathcal{F}^{-1}\{#1\}}
\newcommand{\acc}[1]{\entry{\acs{#1}}{\acl{#1}}}
%\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{multicol}%for multiple columns
\usepackage{etoolbox}

\usepackage{nomencl}
\makenomenclature
\setlength{\nomitemsep}{6pt}

% multiple columns for nomencl
% https://latex.org/forum/viewtopic.php?t=14564
 \renewcommand*{\nompreamble}{\begin{multicols}{2}}
\renewcommand*{\nompostamble}{\end{multicols}}
\setlength{\columnsep}{3em}

\usepackage{graphbox}

\setcounter{secnumdepth}{4}
\usepackage{url}

% https://tex.stackexchange.com/questions/163451/total-number-of-citations
\usepackage{totcount}
\usepackage[nolist,nohyperlinks]{acronym}

\begin{acronym}
    \acro{aplc}[APLC]   {Apodized Phase Lyot Coronagraph}
    \acro{paplc}[PAPLC] {Phase Apodized Phase Lyot Coronagraph}
    \acro  {psf}[PSF]   {Point Spread Function}
    \acro  {iwa}[IWA]   {Inner Working Angle}
    \acro  {owa}[OWA]   {Outer Working Angle}
    \acro  {ao}[AO]     {Adaptive Optics}
    \acro  {fpm}[FPM]   {Focal Plane Mask}
    \acro  {ppm}[PPM]   {Pupil Plane Mask}
    \acro  {hz}[HZ]     {Habitable Zone}
    \acro {fpwfs}[FPWFS]{Focal Plane Wavefront Sensing}
    \acro  {fwhm}[FWHM] {Full Width Half Maximum}
    \acro  {fqpm}[FQPM] {Four Quadrant Phase Mask}
    \acro  {agpm}[AGPM] {Annular Groove Phase Mask}
    \acro  {ovc}[OVC]   {Optical Vortex Coronagraph}
    \acro  {pp}[PP]     {Pupil Plane}
    \acro  {fp}[FP]     {Focal Plane}
    \acro  {sam}[SAM]     {Sparse Aperture Masking}
    \acro  {scar}[SCAR]     {Single-mode Complex Amplitude Refinement}
    \acro  {hci}[HCI]   {High Contrast Imaging}
    \acro  {dm}[DM]     {Deformable Mirror}
    \acro  {wfs}[WFS]   {Wavefront Sensor}
    \acro  {zwfs}[ZWFS] {Zernike Wavefront Sensor}
    \acro  {sphere}[SPHERE]{Spectro-Polarimetric High-contrast Exoplanet REsearch}
    \acro  {scfp}[SCFP] {Science Camera Focal Plane}
    \acro  {smd}[SMD]   {Spatial Mode Demultiplexing}
    \acro  {ncpa}[NCPA] {Non-Common Path Aberration}
    \acro  {mspl}[MSPL] {Mode-selective Photonic Lantern}
    \acro  {elt}[ELT]   {Extremely Large Telescope}
    \acro  {jwst}[JWST] {James Webb Space Telescope}
    \acro  {gmt}[GMT]   {Giant Magellan Telescope}
    \acro  {tmt}[TMT]   {Thirty Metre Telescope}
    \acro  {spp}[SPP]     {Shaped Pupil Plate}
    \acro  {efc}[EFC]     {Electric Field Conjugation}
    \acro  {scc}[SCC]   {Self Coherent Camera}
    \acro  {piaa}[PIAA] {Phase Induced Amplitude Apodization}
    \acro  {piaacmc}[PIAACMC] {Phase Induced Amplitude Apodization Complex Mask Coronagraph}
    \acro  {fast}[FAST] {Fast Atmospheric SCC}
    \acro  {smscc}[SM-SCC] {Spectrally Modulated SCC}
    \acro  {app}[APP]   {Apodizing Phase Plate}
    \acro  {gvapp}[gvAPP]   {grating vector Apodizing Phase Plate}
    \acro  {vvc}[VVC]   {Vector Vortex Coronagraph}
   \acro  {vfn}[VFN]    {Vortex Fibre Nulling}
   \acro  {ravc}[RAVC]  {Ring Apodized Vortex Coronagraph}
    \acro  {hwo}[HWO]   {Habitable Worlds Observatory}
%% Define a custom plural form of an acronym   
    \acrodefplural{psf}[PSFs]   {Point Spread Functions}
    \acrodefplural{dm}[DMs]     {Deformable Mirrors}
    \acrodefplural{wfs}[WFSs]   {Wavefront Sensors}
    \acrodefplural{elt}[ELTs]   {Extremely Large Telescopes}
    \acrodefplural{ncpa}[NCPAs] {Non-Common Path Aberrations}
%% Preferably, put all acronym definitions in one file and load it
%   \input{acros.tex}
\end{acronym}

\newtotcounter{citnum} %From the package documentation
\def\oldbibitem{} \let\oldbibitem=\bibitem
\def\bibitem{\stepcounter{citnum}\oldbibitem}
%%%%

\usepackage{lipsum}

% Metadata Information
\jname{Annu. Rev. Astron. Astrophys.}
\jvol{AA}
\jyear{2025}
\doi{10.1146/TBD}

% autoref formatting
\def\sectionautorefname{Section}
\let\subsectionautorefname\sectionautorefname
\let\subsubsectionautorefname\sectionautorefname

% macros
\newcommand{\apjl}{Astrophysical Journal Letters}
\newcommand{\aj}{Astronomical Journal}
\newcommand{\ao}{Applied Optics}
\newcommand{\procspie}{SPIE Proceedings}
\newcommand{\apj}{Astrophysical Journal}
\newcommand{\apjs}{Astrophysical Journal Supplement}
\newcommand{\pasp}{Publications of the Astronomical Society of the Pacific}
\newcommand{\jgr}{Journal of Geophysical Research}
\newcommand{\aap}{Astronomy and Astrophysics}
\newcommand{\aapr}{Astronomy and Astrophysics Review}
\newcommand{\mnras}{Monthly Notices of the Royal Astronomical Society}
\newcommand{\actaa}{Acta Astronomica}
\newcommand{\nat}{Nature}
\newcommand{\prl}{Physical Review Letters}
\newcommand{\prd}{Physical Review D}
\newcommand{\ssr}{Space Science Reviews}
\newcommand{\araa}{Annual Review of Astronomy and Astrophysics}
\newcommand{\jrasc}{Journal of the Royal Astronomical Society of Canada}
% Symbols
\newcommand{\ydata}{\ensuremath{\boldsymbol{y}}}
\newcommand{\hyperparams}{\ensuremath{\boldsymbol{\phi}}}
\newcommand{\meanparams}{\ensuremath{\boldsymbol{\theta}}}
\newcommand{\dt}{\ensuremath{\tau}}
\newcommand{\amplitude}{\ensuremath{\alpha}}
\newcommand{\lengthscale}{\ensuremath{\lambda}}

\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\project}[1]{\textsf{#1}}

% Comments:
\newcommand{\commentmak}[1]{\textcolor{red}{[MAK: #1]}}
\newcommand{\commentsyh}[1]{\textcolor{red}{[SYH: #1]}}

\newcommand{\notebooksuggestion}[1]{\textcolor{blue}{[Notebook: #1]}}

\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}

% message://%3cBYAPR04MB46634305E3091DE92934A5BA8225A@BYAPR04MB4663.namprd04.prod.outlook.com%3e

% Manuscript due date:  September 15, 2024
% Article allotment: 18,000 words, 200 references

% message://%3cCB3B5076-708A-441A-B38E-4050212CB3EA@strw.leidenuniv.nl%3e
% message:/%3cBYAPR04MB466383143958CB8F10DE8D8E82112@BYAPR04MB4663.namprd04.prod.outlook.com%3e

% about 14,400 words, with 11 figures, 40 pages

% (Estimate the sizes of small figures/tables at 300 words and large ones at 600 words; thus, for every figure/table submitted, please subtract the corresponding number of words from your total allotment. An article length estimator is available online at http://www.annualreviews.org/page/authors/general-information; to access it, select the name of your journal from the drop-down list under Article Preparation and Submission.)

% Your review article should present a critical appraisal of the significant, rather than the total, literature in the field. This overview may include your own work (even if unpublished). The article should be useful to specialists as well as teachers and scholars from other areas.  It should emphasize where research in a given area should go, as well as where it has been, such that it will influence the future course of knowledge. A list of topics and authors planned for Volume 63 will be sent to you approximately five months before the manuscript due date, and you may wish to correspond with authors whose subjects border on your own.

% Document starts
\begin{document}

% Page header
\markboth{Kenworthy \& Haffert}{HCC}

%TC:ignore

% Title
\title{High Contrast Coronagraphy}

%Authors, affiliations address.
\author{Matthew Kenworthy$^1$ and Sebastiaan Haffert$^{1,2}$
  \affil{$^1$Leiden Observatory, Niels Bohrweg 2, Leiden 2300RA, The Netherlands; email: kenworthy@strw.leidenuniv.nl}
  \affil{$^2$University of Arizona, Steward Observatory, 933 N. Cherry Avenue, Tucson, Arizona, United States; email: haffert@strw.leidenuniv.nl}}

% Abstracts should include 3–5 bullet points citing actual conclusions of the review. Please limit the abstract to no more than 200 words, including the bullet points. If using TeX, use a “\hangindent=.3cm$bullet$” command at the beginning of each bullet-point paragraph. [The “\begin{itemize}” environment may require the use of a “hardwired” line return (i.e., the ”\\” command) within the environment, as lines may not automatically return in the compiled version.]
%Abstract
\begin{abstract}
Imaging terrestrial exoplanets around nearby stars is a formidable technical challenge, requiring the development of coronagraphs to suppress the stellar halo of diffracted light at the location of the planet.
%
In this Review, we derive the science requirement for high contrast imaging, give an overview of diffraction theory and the Lyot coronagraph, and define the parameters used in our optimization.
%
We detail the working principles of coronagraphs both in laboratory and on-sky with current high contrast instruments, and detail the required algorithms and processes necessary for terrestrial planet imaging with the extremely large telescopes and proposed space telescope missions.

\begin{itemize}
    \item Imaging terrestrial planets around nearby stars is possible with \\ 
    a combination of coronagraphs and active wavefront control \\
    using feedback from \acp{wfs}.
    \item Ground based 8-40m class telescopes can target the habitable \\ 
    zone around nearby M dwarf stars with contrasts of $10^{-7}$ and \\
    space telescopes can search around solar-type stars with \\
    contrasts of $10^{-10}$.
    \item Focal plane wavefront sensing, hybrid coronagraph designs and \\
    multiple closed loops providing active correction are required \\
    to reach the highest sensitivities.
    \item Polarization effects need to be mitigated for reaching $10^{-10}$ \\ contrasts whilst keeping exoplanet yields as high as possible.
%    \item Ground based telescopes require fast ($\ge$ 1kHz) closed loop \\
%    adaptive optic systems and high density deformable mirrors to \\
%%    minimise the wind-driven halo seen in the science camera focal \\
 %   plane.
    \item Recent technology development, including photonics, MKIDS \\
    and QOD will be folded into HC instruments.
\end{itemize}

\end{abstract}

%Keywords, etc.
\begin{keywords}
 Optics, coronagraphs, exoplanets, high contrast, computational methods
\end{keywords}
\maketitle

%Table of Contents
\tableofcontents

\section{INTRODUCTION}
\label{sec:intro}

% High contrast imaging, Lyot corongraph, 2000's development

%TC:endignore

Initially developed to image the Sun's corona without the need for a Solar eclipse \citep{Lyot33}, one of the most significant science drivers for the latest coronagraphs is in the detection and characterisation of circumstellar material and planets around nearby stars.
%
Young self-luminous gas giant exoplanets have been discovered around young stars \citep[see ][ for a review of these detections]{Zurlo24} both in the nearby Galactic field and further away in young stellar OB associations ranging from 80 to 400 pc distance, typically these exoplanets have luminosities of $10^{-4}-10^{-6}$ of their parent star at angular separations up to a few arcseconds.

% \begin{armarginnote}[]
%   \acc{hci}
%   \acc{fp}
%   \acc{pp}
%   \acc{fpwfs}
%   \acc{wfs}
% \end{armarginnote}

At optical wavelengths, exoplanets are not self-luminous but instead reflect the light of their parent star.
%
For an Earth analogue with similar radius, albedo and effective temperature orbiting around a solar-type star 10 parsecs away, the typical amount of reflected light in the optical is $10^{-10}$ of the central star at a separation of 0.1 arcseconds at maximum elongation.
%
The technical challenge is in distinguishing the light of the parent star from the light of the planet.
%
Planetary systems that are closer to the Sun have two benefits: one that is twice as close as the other will have double the angular separation between the star and planet, and from the inverse square law, four times more flux is received from the planet.
%
For direct imaging, therefore, the closest stars to the Sun are the ones that are studied for the presence of directly imaged exoplanets.
%
On average there are more M dwarf stars close to the Sun than other solar type stars: in a volume limited (20 parsec) sample around the Sun, there are $\sim 140$ solar G-type stars, and on the order of 1900 M-dwarf stars \citep{Kirkpatrick24}.
%
For solar type stars, the contrast required in the optical wavelengths is on the order of $10^{-10}$ for terrestrial planets in the HZ of solar type stars, but for smaller mass stars with lower luminosities, the contrast is $10^{-7}$ for M dwarfs.

%Using Fresnel zones to make a circular null around the star \citep{Angel86} first time you could detect a Jupiter around a sun-like star.

\begin{figure}[ht]
  \centering
  \script{plot_flux_ratio.py}
  \includegraphics[width=1.0\linewidth]{figures/flux_ratio.pdf}
  \caption{Angular separation versus contrast for directly imaged exoplanets.
  %
  The upper right part of the figure shows known self-luminous gas giant planets \citep{Lacy20}.
  %
  The lines show  $5\sigma$ point source contrast limits from recent instruments and surveys.
  %
  %Lines and points are color coded by wavelength of observation. 
  %
  Figure plot and data from \citet{Bailey24}.% and \href{https://github.com/nasavbailey/DI-flux-ratio-plot}{DI-flux-ratio-plot}.
  %
  Grey triangles are the expected contrasts for reflected light from known radial velocity detected exoplanets \citep{Bataltha18}.
  %
  Circles represent reflected light estimates for 1 Earth radius planets, assuming one planet per star within 20 parsecs of the Sun in the Habitable Zone at maximum elongation.
  %
  Grey points are planets that are fainter than 30th magnitude in $V$.
  %
  The color represents the effective temperature of the star.
  %
  The larger the point, the closer the stellar system is to the Sun.
  %
  Reflected light data from \href{https://subarutelescope.org/staff/guyon/04research.web/14hzplanetsELTs.web/catalog.web/content.html}{Guyon (2024) web page}.  
  %{\em ELT goal:} Possible range of near-IR post-processed detection limits for next generation extremely large telescopes. 
% -- HabEx: Goal 5-sigma post-processed contrast.  IWA $\sim$ 2.5 \ld{} @ 450nm; OWA $\sim$ 32 \ld{} at 1micron (source: B. Mennesson, personal communication)
% -- JWST NIRCAM: 5-sigma post-processed [ADI+RDI] contrast curve for F356W-band from program ERS 1386 on HIP 65426. Data inside the nominal IWA of 0.64'' are not displayed (source: Carter+2022)
% -- HST NICMOS: 5-sigma post-processed [KLIP + match filter] contrast curve for F160W-band; this was the BEST contrast curve from the ALICE program (HST program 7226, and others), with typical integration times of 2hr (600-1600s range). (source: E. Choquet, personal communication) Please cite \url{http://adsabs.harvard.edu/abs/2014SPIE.9143E..57C}.
% -- HST STIS: Bar5 coronagraph 5-sigma post-processed [KLIP] contrast curve; 162sec exposure. Photon noise is a significant contributor beyond 0.7''. (source: STIS handbook) This program observed HD 38393 at 9 roll angles with 9 dithers per roll angle. No filter was used, so the bandpass is ~200-1030nm. Total exposure time = 810*.2sec = 2.7 minutes, and is therefore moderately photon limited at large angles. Assuming photon noise adds in quadrature with speckle residuals to produce the KLIP contrast, the photon noise is $>$50\% the amplitude of the speckle noise beyond $\sim$0.7''.
% -- HST ACS: 5-sigma post-processed [simple image difference] contrast curve of 2x100sec Arcturus observation in F606W with 1.8'' occulter. The two exposures were taken 85 minutes apart, to simulate a typical 2-roll (2 orbit) ADI observation. The contrast curve is a simple difference of the images, after registration. (source: J. Krist, personal communication)
% -- SPHERE: 5 sigma post-processed [SDI] contrast curve for an ~1hr integration on Sirius. At separations $<0.7''$ the curve is for IFS YJH, while $>0.7''$ is IRDIS K12; $0.7''$ is the crossover point where IRDIS becomes better than IFS. Integration times: IRDIS = 88 min, IFS = 59min; difference is due to detector overheads. FOV rotation = 106dgr. The SDI reduction assumes the planet-star contrast is constant at all wavelengths. (Source: Vigan et al. 2015 MNRAS 454 129)
% -- GPI: 5-sigma post-processed [KLIP + forward model match filter] contrast curve for H-band IFS mode, 1hr integration. Calculated from an 11min H-band IFS observation of Sirius, reduced with Jean-Baptiste Ruffio's Forward Model Matched Filter code, optimized for L-type objects. The 60min column is $\sqrt(t)$ scaling from the 11min column, for a more equal comparison to the SPHERE 59min IFS contrast curve. (source: B. Macintosh, personal communication).
% -- Roman CGI narrow FOV imaging prediction: Modeled 5-sigma post-processed [RDI\&fpp=2] contrast curve for Band 1 imaging of a V=5 G0V star with the HLC coronagraph. The model observation uses an optimistic estimate for instrument and observatory performance and for 21mo into mission. Integration time is 100hr. Updates include: flight mask, performance tables, bench warping and DM temperature stability, coating reflectivity. Source: \url{https://github.com/hsergi/Roman_Coronagraph_ETC/tree/main/tables/}, 12/02/2021 version.
% -- Roman CGI Single Slit, Prism-based Spectroscopy prediction: Modeled 5-sigma post-processed [RDI\&fpp=1.22] contrast curve for Band 3 spectroscopy of a V=5 G0V star with the SPC bowtie coronagraph. The model observation uses an optimistic estimate for instrument and observatory and for 21mo into mission. Integration time is  400hr. Updates include: flight mask, performance tables, bench warping and DM temperature stability, coating reflectivity. Source: \url{https://github.com/hsergi/Roman_Coronagraph_ETC/tree/main/tables/}, 12/02/2021 version.
% -- Roman CGI wide FOV imaging prediction: Modeled 5-sigma post-processed [RDI\&fpp=2] contrast curve for Band 4 imaging of a V=5 G0V star with the HLC coronagraph. The model observation uses an optimistic estimate for instrument and observatory performance and for 21mo into mission. Integration time is 100hr. Updates include: flight mask, performance tables, bench warping and DM temperature stability, coating reflectivity. Source: \url{https://github.com/hsergi/Roman_Coronagraph_ETC/tree/main/tables/}, 12/02/2021 version.
% -- DI: Selected known self-luminous Directly Imaged (DI) exoplanets with known H-band contrasts. Predicted fluxes at Bands  1 and 3 are either from B. Lacy or from either COND $(T_{eff}\le 1200K)$ or BT-SETTL models. For COND/BT values, WFC3 filters that approximate Roman's coronagraph instrument bands were used (547nm 10\% and 763nm 10\%), because WFC3 colors are already provided with the model grids.
% -- Earth (==1E-10) \& Jupiter (albedo=0.52) at quadrature as seen from 10 pc. (Jupiter albedo: Traub \& Oppenheimer, Direct Imaging chapter of Seager Exoplanets textbook, Table 3)
% -- RV: Predicted reflected light flux ratios at quadrature for known RV planets, from the Imaging Mission Database. We assume clouds with $f_{sed} = 3$. Dark gray triangles signify V $<$ 5 host stars; light grey triangles signify  $5 < V < 6$ host stars. Commented lines are planets that would meet criteria, but whose host stars are known binaries and/or too large in angular diameter. See \url{https://plandb.sioslab.com/about.php} for Imaging Mission Database acknowledgements policy.
}
  \label{fig:nstars}
\end{figure}

%Two regimes: solar analogues at optical wavelengths lead to space based missions, ground based larger aperture telescopes study M dwarf stars that are on average closer to the Sun, and look in the NIR.

%A list of stars suitable for space telescope imaging is listed in \citet{Harada24} based on a catalog derived by

%HPIC is listed in \citet{Tuchow24} and this was derived from the original list of 13,000 stars \citep{Mamajek24}.

%Chris Stark Space telescope yield papers...\citep{Stark14,Stark24}.

The search for life beyond the Earth has focused on the idea that water is an essential part of life cycles elsewhere in the Universe, as it is a polar solvent formed from two elements that are found in abundance throughout the Galaxy.
%
Places where water can exist in its liquid state form prime locations for these searches, notably Earth-like planets and ice moons that have a liquid water ocean underneath an ice layer.
%
The region around a star where liquid water can exist on the surface of a terrestrial planet (with appropriate atmospheric pressure) is referred to as the \acl{hz}; for the Sun this is from 0.9-1.2 au but this can move as the luminosity of stars change with time.

The markers for biosignatures also set the parameters (such as wavelength and bandwidth) that form part of the design decision.
%
Spectra of Earthshine (light reflected from the Earth by the non-Sun lit portion of the Moon) from 0.5 to 2.4 microns show \ce{O2}, \ce{O3}, \ce{CO2}, \ce{CH4} and \ce{H2O} \citep{Turnbull06}, and there are many discussions about the possible biomarker molecules that should be searched for and characterised as evidence for biosignatures \citep[see the reviews of ][]{2016AsBio..16..465S,2017ARAA..55..433K,2018AsBio..18..663S}.
%
It is clear that the unambiguous detection of life will require not one singular detection of a molecule, but will be the combination of several different lines of evidence.
%
We focus on the technical challenges for imaging a rocky terrestrial planet around a nearby star in our Galaxy.

\section{Definition of quantities}

\nomenclature{$i$}{The imaginary unit}

\nomenclature{$c$}{Speed of light in a vacuum}
\nomenclature{$\vec{E}$}{Electric field}
\nomenclature{$\vec{H}$}{Magnetic field}
\nomenclature{$\mathcal{D}$}{Displacement field}
\nomenclature{$\mathcal{B}$}{Magnetizing field}
\nomenclature{$\epsilon$}{Electric permittivity}
\nomenclature{$\epsilon_0$}{Electric permittivity of vacuum}
\nomenclature{$\mu$}{Magnetic permittivity}
\nomenclature{$\mu_0$}{Magnetic permittivity of vacuum}
\nomenclature{$\omega$}{Wavenumber}
\nomenclature{$\vec{k}$}{Wavevector}

\nomenclature{$\lambda$}{Wavelength}
\nomenclature{$\lambda_0$}{Center wavelength in the bandpass}
%\nomenclature{$\delta\lambda$}{d}
\nomenclature{$\Delta\lambda$}{The width of the bandpass}

\nomenclature{$D$}{Diameter of the pupil}

\nomenclature{$n$}{(Complex) refractive index of a macroscopic material}
\nomenclature{$\mathcal{F}_{x,y}[\cdot]$}{Fourier transform operator}
\nomenclature{$\mathcal{F}^{-1}_{x,y}[\cdot]$}{Inverse Fourier transform operator}
\nomenclature{$C_\lambda[\cdot]$}{A general coronagraph propagation operator}

\nomenclature{$\Psi_\lambda[\vec{k}]$}{Coronagraphic image}
\nomenclature{$\phi$}{The phase of the electric field}
\nomenclature{$\alpha$}{The amplitude of the electric field}
\nomenclature{$\Pi$}{The telescope pupil function.}

\printnomenclature

\section{From Maxwell's Equations to Wavefronts}\label{sec:maxwell}
The vast majority of energy from astrophysical objects arrives at our telescopes in the form of electromagnetic radiation.
%
%The electromagnetic waves propagate through space by exchanges between the electric and magnetic fields because a changing electric field induces a magnetic field and vice-versa.
%
This time-dependent interaction is described by Maxwell's equations,

\begin{equation}
\begin{aligned}
\frac{\partial\mathcal{D}}{\partial t} \quad & = \quad \nabla\times\mathcal{H},   & \quad \text{(Faraday's law)} \\[5pt]
\frac{\partial\mathcal{B}}{\partial t} \quad & = \quad -\nabla\times\mathcal{E},  & \quad \text{(Ampere's Law)}   \\[5pt]
\nabla\cdot\mathcal{B}                 \quad & = \quad 0,                         & \quad \text{(Gauss's law)}   \\[5pt]
\nabla\cdot\mathcal{D}                 \quad & = \quad 0.                         & \quad \text{(Coulomb's law)}
\end{aligned}
\end{equation}

This form of Maxwell's equations is in the material form without any charge and current sources.
%
The material form is used to describe the propagation of electromagnetic fields inside matter.
%
This set of equations is completed by describing the particular matter of the medium with the constitutive relations, $D=\epsilon E$ and $B=\mu H$. 
%
Here $\epsilon$ and $\mu$ are the permittivity and magnetic permeability, respectively.
%
The wave equation for electromagnetic waves can be derived by taking the curl of Ampere's law.
%
This gives us the classic wave equation if we assume that the EM wave propagates in isotropic and homogeneous materials,
\begin{equation}
\label{eq:wave_eq}
\begin{aligned}
%\nabla\times\frac{\partial\mathcal{B}}{\partial t} \quad  =& \quad -\nabla\times\nabla\times\mathcal{E} \\
%\frac{\partial\nabla\times\mathcal{B}}{\partial t} \quad  =& \quad -\nabla^2\mathcal{E} \\
%\frac{\partial\nabla\times\mathcal{\mu H}}{\partial t} \quad  =& \quad -\nabla^2\mathcal{E} \\
%\mu\frac{\partial^2 \mathcal{D}}{\partial t^2} \quad  =& \quad -\nabla^2\mathcal{E} \\
\mu \epsilon \frac{\partial^2 \mathcal{E}}{\partial t^2} - \nabla^2\mathcal{E} = 0 .
\end{aligned}
\end{equation}
We consider a purely monochromatic EM wave with frequency $\omega$.
%
The wave function is then $\mathcal{E}=\psi(r) e^{iwt}$ with $\psi(r)$ describing the spatial distribution.
%
Substituting this relation into Equation \ref{eq:wave_eq},
\begin{equation}
\nabla^2\mathcal{E} +\mu \epsilon \omega^2 \mathcal{E} = 0.
\end{equation}
The usual definition of the permittivity and permeability are $\epsilon=\epsilon_r \epsilon_0$ and $\mu=\mu_r \mu_0$ with $\epsilon_r$ and $\mu_r$ the relative permittivity and permeability compared to that of vacuum, $\epsilon_0$ and $\mu_0$.
%
In optics most glasses and materials are defined by their refractive index $n$ which is related to permittivity as $\epsilon_r = n^2$ and many of these are also non-magnetic which means that $\mu_r=1$.
%
Substituting this will give us the classic Helmholtz equation
\begin{equation}
\nabla^2\mathcal{E} + n^2k^2 \mathcal{E} = 0,
\end{equation}
We made use of the fact that the speed of light is $c = \frac{1}{\sqrt{\epsilon_0\mu_0}}$ and that $k = c\omega$ is the wave number.
%
The propagation through an optical system has a preferential direction that is usually defined along the z-axis.
%
The z-axis evolution can be derived by separating the spatial components into the z component and the perpendicular components (x,y),
\begin{equation}
\frac{\partial^2\mathcal{E}}{\partial z^2} = -\nabla_{\perp}^2\mathcal{E}-n^2k^2 \mathcal{E},
\end{equation}
This differential equation can be solved by assuming a plane wave expansion $\mathcal{E}(x,y,z)=e^{i(k_x x + k_y y)}f(z)$ which results in
\begin{equation}
\frac{\partial^2\mathcal{E}}{\partial z^2} = -(n^2k^2 - k_{\perp}^2)\mathcal{E}.
\end{equation}
The solution to this equation is the so called Angular Spectrum Propagator that relates the electric field at any one plane to the electric field at any other,
\begin{equation}
\label{eq:angular_spectrum}
\mathcal{E}(x, y, z') = \mathcal{F}_{x,y}^{-1}\{e^{-ik_z(z'-z)}\mathcal{F}_{x,y}\{\mathcal{E}(x,y,z)\}\}.
\end{equation}

Here the $z$ component of the wave vector is defined as $k_z=\sqrt{n^2k^2 - k_{\perp}^2}$ and $\mathcal{F}_{x,y}^{(-1)}$ is defined as the (inverse) Fourier transform over the x and y coordinates.
%
While Equation \ref{eq:angular_spectrum} describes the full propagation from one plane to another, it is quite unwieldy to use and does not provide much physical insight.
%
For many optical systems it is sufficient to analyze the paraxial performance.
%
The paraxial approximation assumes that the plane waves make small angles with respect to the z-axis which means that the $x$ and $y$ wave vector components are $k_x,k_y<<1$.
%
In this regime the propagation factor $k_z=\sqrt{n^2k^2 - k_{\perp}^2}\approx nk - \frac{k_{\perp}^2}{2nk}$ and the Fresnel propagation equation becomes
\begin{equation}
\label{eq:angular_spectrum2}
\mathcal{E}(x, y, z') = e^{-ink(z'-z)} \mathcal{F}_{x,y}^{-1}\{ e^{-i\frac{k_{\perp}^2}{2nk}} \mathcal{F}_{x,y}\{\mathcal{E}(x,y,z)\}\}.
\end{equation}
The real space solution that is derived from the propagation equation is the classical Fresnel diffraction equation,
\begin{equation}
\label{eq:fresnel_diffraction}
\mathcal{E}(x, y, z') = \frac{e^{-ink(z'-z)}}{\lambda z} \iint_{-\infty}^{\infty} \mathcal{E}(u, v, z) e^{\frac{ik\left[(x - u)^2 + (y - v)^2\right]}{2 (z' - z)}} \mathrm{d}u \mathrm{d}v.
\end{equation}
The far-field approximation ($z \gg x, y$) and the substitution $\theta_x = \frac{x}{\lambda z}$, $\theta_y = \frac{y}{\lambda z}$ results in the Fraunhofer diffraction integral,
\begin{equation}
\label{eq:fraunhofer_diffraction}
\mathcal{E}(\theta_x, 
\theta_y) \propto \iint_{-\infty}^{\infty} \mathcal{E}(u, v) e^{-i2\pi(\theta_x u + \theta_y v)} \mathrm{d}u \mathrm{d}v.
\end{equation}
This shows that the far-field distribution of an electromagnetic wave is it's Fourier transform. A perfectly aligned lens, or the mirrors of a telescope, brings rays that come from infinity to the focal point. This is identical to a far-field transform, and therefore the operation of a lens can be described by the Fraunhofer diffraction integral.
%$$E(\mathbf{r},t)=E_0(\mathbf{r})e^{i(\mathbf{k}.\mathbf{r}-\omega t)}$$

%Maxwell's equations describe the time-dependent interaction between static and moving electric charges, electric fields and magnetic fields.

%When a star is imaged with a large ground based telescope the detector does not see a point source with all flux concentrated into one pixel, but instead the stellar flux is distributed across a finite area.%actually an infinite area because band-limited signals have an infinite support. There is no end to the Airy pattern.

%
%This is due to the wave-like nature of electromagnetic radiation.

% ENERGY PROPAGATION
%Energy is stored in both the electric and magnetic fields.
% WAVE SOLUTIONS
%One solution to these equations are second-order differential wave equations, which describe a periodic change in the electric and magnetic field strength throughout a given volume.
%
%In the absence of any free electrical charges, these show that, energy is propagated in a direction along their direction of motion. BLAH NOT TRUE FOR CALCITE...
% ENERGY IN E FIELDS
%The majority of energy is stored in the electric field, and since the magnetic field strength follows the electric field strength we only talk about the time and space evolution of the electric field.

%The time-varying electric field strength of an electromagnetic plane wave at time $t$ is described by:

%$$E(\mathbf{r},t)=E_0(\mathbf{r})e^{i(\mathbf{k}.\mathbf{r}-\omega t)}$$
%where $\mathbf{r}$ is a point in three-dimensional space, $\mathbf{k}$ is a unit vector pointing in the direction of the wave propagation, and $\omega$ is the angular frequency of the wave.
%
%The angular frequency and wavelength of the wave is related by $\omega = 2\pi c/\lambda$ where $c$ is the propagation speed in free space.
%
% PHASE only applies to a periodic wave!
